Attribute fusion in a latent process model for time series of graphs

### 2011-05-11 ssp2011.tex
Fixed proof of max degree to use large deviation bounds

    a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}}}{4 \log{n}} -
    \frac{\log{2\pi^{1/2}}}{2 \log{n}} \Bigr) \\ 

@@

  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(1)}(v;t), \dots,
  \Gamma^{(K)}(v;t))$ for $t < t^{*}$ is distributed as a multinomial
  with $n-1$ trials and probability vector $\pi_{00}$. The folllowing
  statements are made under the assumption that $n \rightarrow \infty$
  for fixed $K$. By the multivariate central limit theorem, we have

@@

    \frac{\bm{\Gamma}(v;t) - (n-1) \pi_{00}}{\sqrt{n-1}}
    \rightsquigarrow \mathcal{N}(0, (\mathrm{diag}(\pi_{00}) -
    \pi_{00} \pi_{00}^{T}))

@@

  Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t) \rangle$
  and we have
      \rangle}{\sqrt{n-1}} \rightsquigarrow \mathcal{N}(0, \langle \lambda, \eta_{00} \lambda \rangle)
  Therefore, $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
      \rangle}} \rightsquigarrow N(0,1)$. We can thus consider the
  degree sequence of $G(t)$ for $t < t^{*}$ as a sequence of {\em
    dependent} Gaussian random variables. By an argument analogous to
  the argument for Erd\"{o}s-Renyi random graphs in \cite[\S
  among the $d_{\lambda}(v,t)$ can be ignored. Let us define
  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
  the sample maximum of Gaussian random variables converges weakly to
  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. We thus obtain
Eq.~\eqref{eq:14} for $t < t^{*}$. The case when $t = t^{*}$ can be
derive in a similar manner. We first apply Lemma 3.1 in
\cite{rukhin:_limit_distr_graph_scan_statis} to show that if $m =

@@

\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$.  
We then show, again by the multivariate

@@

  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows that

@@

By the multivariate CLT, we have

@@

\eta_{00} \lambda \rangle$ and by the CLT, we have

@@

l_{\xi}, p_{10} \Bigr)$. By the CLT, we have

@@

the locality statistics for an unattributed kidney and egg model.
\bibliography{ssp2011}
\end{document}

>>>>

    a_n &= (2 \log{n})^{1/2}\Bigl(1 - \frac{\log{\log{n}} + \log{4\pi}}{4 \log{n}} \Bigr) \\ 

@@

  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(k)}(v;t))_{k=1}^{K}$
  for $t < t^{*}$ is distributed as a multinomial with $n-1$ trials
  and probability vector $\pi_{00}$. The following statements are
  made as $n \rightarrow \infty$ for fixed
  $K$. Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t)
  \rangle$ and
  thus, by the central limit theorem, we have
    \label{eq:17}
      \rightsquigarrow \mathcal{N}(0, 1)
    We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
    as a sequence of {\em dependent} normally distributed random
    variables. By an argument analogous to the argument for
    Erd\"{o}s-Renyi random graphs in \cite[\S
    among the $d_{\lambda}(v,t)$ can be ignored. $d_{\lambda}(v;t)$,
    when normalized, can thus be considered as a sequence of
    independent random variables from the standard normal in the
    limit. It is widely known that the sample maximum of standard
    normal random variables converges weakly to a Gumbel distribution
    \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is,
    however, not clear whether the convergence of
    $\Delta_{\lambda}(t)$ to a Gumbel distribution continues to hold
    under the composition of weak convergence as
    outlined above. We avoid this problem by showing
    directly that 
      \label{eq:22}
  \mathbb{P}\Bigl(\tfrac{\Delta_{\lambda}(t) - (n-1)
        \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle
          \lambda, \eta_{00} \lambda \rangle}} \leq a_n + b_n x\Big)
      \rightarrow 
      e^{-e^{-x}} 
    Let $\zeta_v = \tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
        \rangle}}$ and $F_n(u) = \mathbb{P}(\zeta_v \leq u)$. If $n
    \rightarrow \infty$ and $u = o(\sqrt{n})$, we have the
    following large deviations result \cite[Theorem~2, \S
    XVI.7]{feller71:_introd_probab_theor_its_applic}.
      \label{eq:23}
      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \exp\Bigl(u^2
      h(\tfrac{u}{\sqrt{n}})\Bigr) \Bigl[1 + O(\tfrac{u}{\sqrt{n}}) \Bigr]
    where $h(z)$ is a power series defined by

@@

      z^{2} h(z) = h_0 z^3 + h_1 z^4 + \dots

@@

    and the $h_i$ are constants. Letting $u_n = a_n + b_n x$ in
    Eq.~\eqref{eq:23}, we have
      \label{eq:24}
     1 - F_n(u_n) = (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
     O(\tfrac{u_n^{4}}{n}))
    for some constant $C$. We therefore have
      \label{eq:25}
      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n}
      \\
      &= \Bigl[\Phi(u_n) + \Phi(u_n) 
      \tilde{O}(\tfrac{1}{\sqrt{n}})\Bigr]^{n} \\
      &= \Bigl[\Phi(u_n) + \tilde{O}(\tfrac{1}{n^{3/2}})\Bigr]^{n} \\
      &= (\Phi(u_n))^{n} + \tilde{O}(\tfrac{1}{n^{1/2}}) \\
      & \rightarrow e^{-e^{-x}} 
    where $\tilde{O}$ denote that the powers of $u_n =
    O(\log{n})$ are ignored. Eq.~\eqref{eq:22} is established and
    we obtain the limiting Gumbel distribution for
    $\Delta_{\lambda}(t)$ for $t < t^{*}$ in Eq.~\eqref{eq:14}.
    % Now $n(1 - \Phi(u_n)) = \exp(-x)(1 + o(u_n^{-1 + \theta}))$ for
    % some small $\theta > 0$. We thus have
    % \begin{equation}
    %   \label{eq:26}
    %   \begin{split}
    %   \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= \Bigl[ \Phi(u_n) - C
    %   u_n^{3}n^{-3/2} e^{-x}(1 + o(u_n^{-1 + \theta})) + O(u_n^{4}/n)
    %   n^{-1} e^{-x} \Bigr]^{n} \\
    %   &= (\Phi(u_n))^{n}\Bigl[1 - C u_n^{3}n^{-1/2} e^{-x}(n \Phi(u_n))^{-1} +
    %   o(u_n^{-4 + \theta})n^{-2} e^{-x}\Bigr]^{n} \\
    %   &= (\Phi(u_n))^{n} - C u_n^{3}n^{-1/2} e^{-x} (\Phi(u_n))^{n-1} +
    %   o(u_n^{-4 + \theta}n^{-1/2}) e^{-x} \\
    %   &= (1 + o(1)) \Phi(u_n)^{n}
    %   \end{split}
    % \end{equation}
    % where the term $o(1)$ can be made to be independent of
    % $x$. Furthermore, we can verify that $\Phi(u_n)^{n} \rightarrow
    % e^{e^{-x}}$ and thus Eq.~\eqref{eq:22} is established. 
 % Let us define
 %  $\xi_s$ for $s \in \mathbb{R}$ as the number of vertices $v$ such
 %  that $\tfrac{d_\lambda(v;t) - (n-1) \langle \lambda, \pi_{00}
 %    \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
 %  \geq s$. Note that $\xi_s \leq k$ only if there are at most $k$
 %  vertices with $\tfrac{d_{\lambda}(v;t) - (n-1) \langle \lambda,
 %    \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
 %      \rangle}} \geq s$. Thus, $\tfrac{\Delta_{\lambda}(v;t) - (n-1)
 %    \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda,
 %      \eta_{00} \lambda \rangle}} < s$ only if $\xi_s = 0$. Because
 %  the sample maximum of Gaussian random variables converges weakly to
 %  a Gumbel \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis},
 %  by taking $n \rightarrow \infty$ followed by $s \rightarrow \infty$,
 %  we can show that $\tfrac{\Delta_{\lambda}(v;t) - (n-1) \langle \lambda,
 %  \pi_{00} \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda
 %    \rangle}} \rightsquigarrow \mathcal{G}(a_n, b_n)$. 
The case when $t = t^{*}$ can be
derive in a similar manner. We first show that if $m =

@@

\max_{v \in [m]}{d_{\lambda}(v;t^{*})}$ \cite[Lemma
3.1]{rukhin:_limit_distr_graph_scan_statis}.  
We then show, again by the 

@@

  \mu_2}{\sigma_2} \rightsquigarrow N(0,1)$. It then follows, similar
to our previous reasoning for the case where $t < t^{*}$, that

@@

By the central limit theorem, we have

@@

\eta_{00} \lambda \rangle$ and again by the central limit theorem, we have

@@

l_{\xi}, p_{10} \Bigr)$. By the central limit theorem, we have

@@

the locality statistics for an unattributed kidney and egg model. We
thus define $Y(v) = Y_{\zeta}(v) + Y_{\xi}(v) + Y_{\omega}(v)$
where $Y_{\zeta}(v) \sim C_{11}
\mathrm{Bin}(\tbinom{d_{\zeta}(v;t)}{2}, p_{11})$ and $Y_{\xi},
Y_{\omega}$ are defined accordingly. Let $G \sim \kappa(n,m,p_{11},
p_{10}, p_{00})$ be an unattributed kidney-egg graph with the
probability of egg-egg, egg-kidney, and kidney-kidney connections
being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. Let $M(v)$ and
$W(v)$ denote the number of vertices adjacent to $v$ in $[m]$ and $[n]
\setminus [m]$, respectively. $D(v) = M(v) + W(v)$ is then the degree
of $v$ in $G$. We now show two
inequalities relating the tail distribution of 
$\Delta(G)$ and $\Upsilon(G) = \max_{v \in V(G)} Y(v)$.
  \label{eq:27}
    \limsup \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim
   \mathbb{P}( \Delta(G) \geq N_\kappa) \\
   \label{eq:30}
  \liminf \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(
  \Delta(G) \geq N_{\kappa})
\begin{proof}[Eq.~\eqref{eq:27}]
 Let $C^{*} = \max\{C_{11},
C_{10}, C_{00}\}$ and $d_{n,m} = \sqrt{2 a_{n,m}/C^{*}}$. We first
note that
\Upsilon(G) \geq a_{n,m} \Rightarrow C^{*} \tbinom{D(v)}{2} \geq
a_{n,m} \Rightarrow D(v) \geq d_{n,m} 
Let us define $h(v) = \mathbb{E}[Y(v)]$, i.e., 
  h(v) = C_{00}p_{00} \tbinom{D(v)}{2} &+ (C_{11} p_{11} - C_{00}
  p_{00}) \tbinom{M(v)}{2} \\ &+ (C_{10} p_{10} - C_{00} p_{00}) M(v) W(v)
We then have
    \label{eq:31}
    \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &= \mathbb{P}\Bigl( \bigcup_{v
      \in V(G)} Y(v) \geq a_{n,m}\Bigr) \\
    &= \mathbb{P}\Bigl( \bigcup_{v
      \in V(G)} Y(v) \geq a_{n,m}, \, D(v) \geq d_{n,m} \Bigr) \\
    &= P_1 + P_2
    \vartheta_n &= C_{00} \Bigl[ \tbinom{n}{2} p_{00} (1 -
    p_{00})\Bigr]^{1/2} \log{n} \\
    P_1 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m}, h(v) \geq
    a_{n,m} - \vartheta_n) \\
    P_2 &= \mathbb{P}(\bigcup_{v \in V(G)} D(v) \geq d_{n,m},
    Y(v) - h(v) \geq \vartheta_n)
  We now show that $P_2$ is negligible as $n \rightarrow \infty$. To
  proceed, let $p_{e,f} = \mathbb{P}(M(v) = e, W(v) =
f)$. $P_2$ can then be bounded as follows
    P_2 & \leq n \sum_{D(v) \geq
        d_{n,m}}{\mathbb{P}\biggl( Y(v) - \mathbb{E}[Y(v)] \geq
        \vartheta_n \biggr) p_{e,f}}
  \\
  &= n \sum_{D(v) \geq d_{n,m}}{\mathbb{P}\biggl(
    \tfrac{Y(v) - \mathbb{E}[Y(v)]}{\sqrt{\mathrm{Var}[Y(v)]}} \geq
    \tfrac{\vartheta_n}{\sqrt{\mathrm{Var}[Y(v)]}} \biggr) p_{e,f}} \\
    &\leq n \sum_{D(v) \geq d_{n,m}} (1 + o(1)) \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\
    &= o(1)

\end{proof}
\end{proof}
\bibliography{ssp2011}
\end{document}
